Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/correlated-sicm-and-fm.tex
reworked

% Assume a figure here which shows the different degrees of correlation
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
  \caption{%
    \textbf{Combining SICM and wide-field fluorescence microscopy.}
    \textbf{a:}
    \textbf{b:} FM image of presynaptic nerve terminals stained with
    FM1-43. \textbf{c:} Overlay of the FM-image and two SICM recordings of the
    same region. \textbf{d:} 3D-representation of the lower right SICM
    recording from c.
    \textbf{b--d:} Reprinted with permission from ref \cite{Scheenen2015}.
  }
  \label{fig:sicm+fm}
\end{figure}

@@

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Scheenen2015} (Fig.~\ref{fig:sicm+fm}b--d) or to
identify the neuron which had been investigated by SICM-guided patch-clamp of
synaptic boutons \cite{Novak2013}.

Furthermore, it has been used to first identify primary cilia in a cell
culture and subsequently use SICM to reveal whether the selected cilium was
extending into the extracellular space or was embedded in the cell, an
information which could not be retrieved by using FM alone \cite{Zhou2018}.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{a:} SICM recording of a cardio-myocyte which was subsequently
    tested for the occurrence of the $\beta_1$-AR at the crest (\textbf{b})
    and at the T-tubule (\textbf{c}). 
    \textbf{d:} SICM recording of a cardio-myocyte which was subsequently
    tested for the occurrence of the $\beta_2$-AR at the crest (\textbf{d})
    and at the T-tubule (\textbf{e}).
    Reprinted with permission from ref. \cite{Nikolaev2010}.
  }
  \label{fig:nikolaev2010}
\end{figure}

Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
crests (Fig.~\ref{fig:nikolaev2010}a, d). By first recording the topography
and subsequently moving the SICM pipette to either a T-tubule or a crest,
followed by the local application of agonists of either the $\beta_1$- or
$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
and yellow fluorescent protein, coupled to a Förster resonance energy transfer
(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}b, c, e, f), it was
shown that the distribution of the $\beta_2$-AR was altered in failing
cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
investigate the effect of partial mechanical unloading, showing that it
reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
approach was extended to use a FRET-based reporter of cyclic GMP, showing that
a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
\cite{Schobesberger2020}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm2}
  \caption{%
    \textbf{Combining SICM and confocal fluorescence microscopy.}
    \textbf{a:} Schematic illustration of the data acquired by combining SICM and confocal FM.
    \textbf{b:} 
    	(left:) Topography of a neuronal network.
    	(center:) Fluorescence of the same neuronal network as depicted on the left.
    	(right:) Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
    	the left and middle image.
    Reprinted with permission from ref \cite{Novak2013}.
  }
  \label{fig:sicm+cfm}
\end{figure}

@@

SICM and confocal FM have been combined for the first time by Korchev et al.
\cite{Korchev2000} in 2000. The group used this combination to verify the
volume measurements obtained by SICM. Just a year later, further development
of this combination enabled simultaneous acquisition of Ca\textsuperscript{2+}
imaging and topography data \cite{Shevchuk2001}.
% Afterwards, many different
% studies using a combination of SICM and confocal FM were published:

@@

% ich würde hier etwas zu potentiellen z-stacks + SICM sagen wollen, das hat
% ja meines Wissens nach noch niemand gemacht...
The applications reviewed above used only a single confocal layer. Yet,
a combination of SICM and $z$-stacking confocal FM could be used to yield more
correlating data. After imaging the entire volume that is scanned by SICM, the
data could be aligned and non-correlating data could be separated from
correlating data. If stage scanning would be omitted, the two measurements
could be performed simultaneously, but not synchronously.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}

  \caption{%
    \textbf{Two setups for a SSC microscope.}
    \textbf{a:} Diagram of the combined setup with an $x,y,z$ sample scanner.
    \textbf{b:} Diagram of the combined setup with a $x,y$ sample scanner and
    a $z$-probe and objective scanner. 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sscm_setup}
\end{figure}

@@

In contrast, the second setup (Fig.~\ref{fig:sscm_setup}b) uses the sample
stage to position the sample in $x$- and $y$-direction only while objective
and probe are positioned by additional piezo elements in $z$-direction. Thus,
when the surface is detected by the SICM pipette,  the position of
the confocal spot has to be adjusted by the objective positioning piezo subsequently.

@@

Switching from three-axis stage scanning to $z$-movement of the pipette
allowed for faster scan rates as the resonant frequency of the 3D
piezo-actor acted as a limiting factor. Additionally, usage of three
piezo-elements on the same platform led to cross-talk and consequentially
artefacts in the SICM data \cite{Shevchuk2013}.

Both setups keep the probe-objective distance constant and enable the
acquisition of a fluorescence image and a topography of the sample surface in
the same scan. Photobleaching is equalized for every point of the sample
allowing quantitative analysis of the FM data.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
  \caption{%
    \textbf{Combining SICM and SCM.}
    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
    \textbf{b:} Simultaneously acquired topographic and fluorescence data of fluorescent Cy3-labeled 
    VLPs adsorbed to the surface of Cos-7 cells. Reprinted with permission from ref \cite{Gorelik2002a}.
    \textbf{c:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
    	\textit{Left:} Cell surface topography. 
    	\textit{Center:} Fluorescence recording of the cell shown left. 
    	\textit{Right:} 3D overlay of topographical and fluorescent recordings. 
    Reprinted with permission from ref \cite{Shevchuk2008}.
    \textbf{d:} Live Cos-7 cells sequentially scanned by SSCM. Overlays of simultaneously obtained 
    topographic and fluorescence scans. Fluorescence imaging was started 2\,h 17\,min after the first 
    SICM scan as indicated by the red star. Fluorescent VLPs were added at 2\,h 40\,min. 
    Reprinted with permission from ref \cite{Gorelik2002}.
  }
  \label{fig:sicm+scm}
\end{figure}

As the SICM and SCM data sets are recorded simultaneously, all data points inherently have a
correlating data point in the other set. This immediate correlation, schematically illustrated in
Fig.~\ref{fig:sicm+scm}a, allows not only for correlating studies in fixed
samples (Fig.~\ref{fig:sicm+scm}c), but also studies of dynamics in live
samples (Fig.~\ref{fig:sicm+scm}d).\todo{Improve paragraph}

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
the differentiation of stem cells \cite{Gorelik2008} and the correlation of
topography and T-tubule distribution \cite{Lyon2012} or topography and
mitochondria localization and appearance \cite{Miragoli2016} in healthy and 
heart-failure cardiomyocytes. Furthermore, it has been utilized in 
studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged clathrin
light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
maturation and internalisation of clathrin coated pits \cite{Ali2019}.

% Bis hier

% \subsection{Nanoinjection of fluorescently labeled molecules}

% Nevertheless SICM does not necessary being used for investigating the topography of a cell, 
% the nanopipette of a SICMic could be also used for the targeted deposition of molecules, like 
% fluorescently-labeled single stranded-DNA molecules \cite{Ying2002,Hennig2015}. The nanopipette 
% could be also used for nanoinjection of fluorescently labeled molecules into living cells 
% \cite{Hennig2015a}. The SICM was therefore combined with wide-field and direct stochastic 
% optical reconstruction microscopy (dSTORM), and mitochondria, actin and DNA could be successfully 
% stained. One problem with the nanoinjection was that artifacts, due to the holes that were 
% introduced into the membranes, could occur \cite{Hennig2015a}.

% The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
% combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
% In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
% the diffusion of single molecules over different regions at a spermatozoa were investigated.

% The SICM-nanopipette could be also used for investigating membrane rafts 
% \cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
% functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
% focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
% was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.

% Another example for a SICM-nanopipette based manipulation could be found in the study on the 
% generation and distribution of plasma-derived extracellular vesicles (PEVs) on MDA-MB-231 and U87 
% cells. Here the nanopipette were used for both, investigating the topography and for inducing the 
% generation of the PEVs. Additionally the SICM was build up onto a confocal microscope, which could 
% be used for the detection of Calcium \cite{Wang2020}.

% % Piper2006 -> PMID: 17177370
% The SICM-nanopipette could be also used as a nanosensor for pH- or ionic concentration changes 
% \cite{Piper2006}. In this study fluorophores were trapped in the nanopipette and react on changes 
% of the pH value or the concentration of ions with alterations in the detected fluorescence signal.

% Dieser Abschnitt passt nicht so wirklich zu Fluoreszenz-Mikroskopie! Vielleicht noch so was 
% schreiben, wie „SICM kann nicht nur mit Fluoreszenz mikroskopischen Methoden kombiniert werden, 
% sondern kann auch mit … kombiniert werden!? Sonst kann der einfach auch weg. Mal gucken.

% By using a special illumination system consisting of a light emitting diode (LED) light ring, SICM 
% could also being combined with condenser-free phase contrast, darkfield and brightfield images and 
% even Rheinberg illuminations were possible \cite{Webb2014}.

>>>>

% Assume a figure here which shows the different degrees of correlation
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
  \caption{%
    \textbf{Combining SICM and wide-field fluorescence microscopy.}
    \textbf{a:} Sketch of the data obtained by combining SICM and wide-field
    FM. 
    \textbf{b:} (left) FM image of a cilium in a RPE-1 cell, (right) SICM recording of
    the area marked by the dashed rectangle. The cilium is not visible since
    it is located benaeth the cell membrane \textbf{c:} (left) FM image of a
    cilium in a MDCK cell, (right) SICM recording of the
    region marked by the dashed rectangle. The cilium is clearly visible since
    it protrudes into the extracellular space.
    \textbf{b, c:} Reprinted with permission from Yuanshu Zhou, Masaki Saito,
    Takafumi Miyamoto, et al.: \emph{Nanoscale Imaging of Primary Cilia with
      Scanning Ion Conductance Microscopy.} Anal. Chem. 2018, 90, 4,
    2891–2895. Copyright 2018 American Chemical Society.
  }
  \label{fig:sicm+fm}
\end{figure}

@@

So far, the combination of SICM and wide-field FM has been used to find a
region of interest such as an area containing active synapses in a culture of
a neuronal network \cite{Scheenen2015} or to
identify the neuron which had been investigated by SICM-guided patch-clamp of
synaptic boutons \cite{Novak2013}.

Furthermore, it has been used to first identify primary cilia in a cell
culture and subsequently use SICM to reveal whether the selected cilium was
extending into the extracellular space or was embedded in the cell
(Fig.~\ref{fig:sicm+fm}b, c), an
information which could not be retrieved by using FM alone \cite{Zhou2018}.

Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
crests. By first recording the topography
and subsequently moving the SICM pipette to either a T-tubule or a crest,
followed by the local application of agonists of either the $\beta_1$- or
$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
and yellow fluorescent protein, coupled to a Förster resonance energy transfer
(FRET) based reporter of cyclic AMP, it was
shown that the distribution of the $\beta_2$-AR was altered in failing
cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
investigate the effect of partial mechanical unloading, showing that it
reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
approach was extended to use a FRET-based reporter of cyclic GMP, showing that
a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
\cite{Schobesberger2020}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+cfm2}
  \caption{%
    \textbf{Combining SICM and confocal fluorescence microscopy.}
    \textbf{a:} Schematic illustration of the data acquired by combining SICM and confocal FM.
    \textbf{b:} 
    	(left:) Topography of a neuronal network.
    	(center:) Fluorescence of the same neuronal network as depicted on the left.
    	(right:) Overlay of topography and fluorescence of two regions of interest (ROI 1, ROI 2) from
    	the left and middle image.
    Reprinted with permission from P. Novak, J. Gorelik, U. Vivekananda, et
    al.: \emph{Nanoscale-Targeted Patch-Clamp Recordings of Functional
      Presynaptic Ion Channels.} Neuron 2013, 79, 1067--1077.
  }
  \label{fig:sicm+cfm}
\end{figure}

@@

SICM and confocal FM have been combined for the first time by Korchev et al.
\cite{Korchev2000} in 2000. The group used this combination to verify the
volume measurements obtained by SICM. Just a year later, further development
of this combination enabled simultaneous acquisition of Ca\textsuperscript{2+}
imaging and topography data \cite{Shevchuk2001}.

@@

The applications reviewed above used only a single confocal layer. Yet,
a combination of SICM and $z$-stacking confocal FM could be used to yield more
correlating data. After imaging the entire volume that is scanned by SICM, the
data could be aligned and non-correlating data could be separated from
correlating data. If stage scanning would be omitted, the two measurements
could be performed simultaneously, but not synchronously.

@@

\begin{figure}
  \centering
  \includegraphics{gr/correlating/sscm_setup}

  \caption{%
    \textbf{Two setups for a SSC microscope.}
    \textbf{a:} Diagram of the combined setup with an $x,y,z$ sample scanner.
    \textbf{b:} Diagram of the combined setup with a $x,y$ sample scanner and
    additional $z$-scanners for probe and objective. 
  }
  \label{fig:sscm_setup}
\end{figure}

@@

In contrast, the second setup (Fig.~\ref{fig:sscm_setup}b) uses the sample
stage to position the sample only in $x$- and $y$-direction while objective
and probe are positioned by additional piezo actors in $z$-direction. Thus,
when the surface is detected by the SICM pipette, the position of the confocal
spot has to be adjusted by the objective positioning piezo actor subsequently.

@@

Switching from three-axis stage scanning to $z$-movement of the pipette and
objective allowed for faster scan rates since the resonant frequency of the 3D
scanning stage limited the recording velocity. Additionally, usage of three
piezo-actors on the same platform led to cross-talk and consequentially
artefacts in the SICM data \cite{Shevchuk2013}.

Both setups keep the probe-objective distance constant and enable the
acquisition of a fluorescence image and the topography of the sample surface in
the same scan.

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+scm}
  \caption{%
    \textbf{Combining SICM and SCM.}
    \textbf{a:} Schematic illustration of the correlating data acquired by SSCM.
    \textbf{b:} SSCM recordings of fixed clathrin-GFP transfected Cos-7 cells. 
    	(left:) Cell surface topography. 
    	(center:) Fluorescence recording of clathrin in the cell shown left. 
    	(right:) 3D overlay of topographical and fluorescent recordings. 
    Reprinted from Shevchuk, A.I., Hobson, P., Lab, M.J., et al.: \emph{Endocytic
    pathways: combined scanning ion conductance and surface confocal
    microscopy study.} Pflugers Arch - Eur J Physiol 2008, 456, 227–235 with permission.
  }
  \label{fig:sicm+scm}
\end{figure}

As the SICM and SCM data sets are recorded simultaneously, all data points
inherently have a correlating data point in the other set, as illustrated in
Fig.~\ref{fig:sicm+scm}a. This allows for determining the distribution of
proteins in the proximity of the cell membrane (Fig.~\ref{fig:sicm+scm}b).

First, SSCM  has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
\cite{Gorelik2002a}.

Furthermore, it has been utilized in studies investigating endocytotic
pathways \cite{Shevchuk2008a} (Fig.~\ref{fig:sicm+scm}b), besides others
revealing an alternative closing mechanism for clathrin-coated pits by
recording topography simultaneously with the fluorescence of tagged
actin-binding protein and the tagged clathrin light-chain
\cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed
the effect of mutations in the Dynamin~2 gene on the maturation and
internalisation of clathrin coated pits \cite{Ali2019}.

\begin{figure}
  \centering
  \includegraphics{gr/correlating/SSCM-np}
  \caption{%
    \textbf{Investigation on nanoparticle uptake by SSCM.}  \textbf{a:} Height
    profile of a section of a AT1-like cell treated with 200\,nm fluorescent
    nanoparticles.  \textbf{b:} Slope representation of the area shown in a.
    \textbf{c:} Surface fluoresecence of the same area.  \textbf{d:} Overlay
    of surface fluorescence and slope representation.  Yellow arrowheads mark
    nanoparticles that co-localise with membrane protrusions (white
    arrowheads), blue arrowheads mark nanoparticles being in the process of
    internalisation, green arrowheads mark fully internalised nanoparticles.
    Reprinted with permission from P. Novak, A Shevchuk, P. Ruenraroengsak, et
    al.: \emph{Imaging Single Nanoparticle Interactions with Human Lung Cells
      Using Fast Ion Conductance Microscopy.} Nano Lett. 2014, 14, 3,
    1202–1207. Copyright 2014 American Chemical Society.}
  \label{fig:sscm-np}
\end{figure}

SSCM was used to characterise the nanoparticle uptake by primary human alveolar
epithelial type 2 (AT2) and by immortalized AT2 cells. Only the latter showed
a strong tendency to internalise nanoparticles. Since, furthermore, the
immortalized cells exhibited several characteristics of alveolar
epithelial type 1 (AT1) cells, it was suggested that AT1 cells play a pivotal
role in the translocation of nanometer-sized particles in the lung
\cite{Kemp2008}.

Figure~\ref{fig:sscm-np} shows nanoparticles in the proximity of the surface of
AT1-like cells at three different stages of the internalisation: co-localised
with membrane protrusions (yellow and white arrowheads, respectively), in the
process of internalisation (blue arrowheads) and fully internalised (green
arrowheads). An improvement of the scanning velocity by the addition of a stiff,
short-range piezo actor onto the pipette positioning piezo actor allowed to
follow the internalisation process with a temporal resolution of 15 seconds in
detail \cite{Novak2014}.

Furthermore, SSCM was used for investigating the differentiation of stem cells
\cite{Gorelik2008} and the correlation of topography and T-tubule distribution
\cite{Lyon2012} or topography and mitochondria localisation and appearance
\cite{Miragoli2016} in healthy and heart-failure cardiomyocytes.
